EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-05-17 draft.tex
Minor typographic changes

% Mention cost here - JJ
% I putted earlier literally at the end of the section :) - M

@@

\begin{table}[h!tbp]
  \small
  \caption{Parameters used in the experiments with ten populations
  }
  \label{tab:params:10}
  \vspace{0.25cm}
  \centering
  \small
  \begin{tabular}{|l|c|c|c|c|c|c|}
    \hline
    Dimension        & 2  & 3  & 5  & 10 & 20  & 40  \\ \hline
    Generations      & 40 & 25 & 28 & 50 & 66  & 80  \\ \hline
    Population Size  & 50 & 60 & 60 & 70 & 100 & 125 \\ \hline
    Populations      & 10 & 10 & 10 & 10 & 10  & 10  \\ \hline
    Iterations       & 10 & 20 & 30 & 30 & 30  & 40  \\ \hline  
  \end{tabular}
\end{table}
%
\begin{table}[h!tbp]
  \small
  \caption{Parameters used in the experiments with five populations
  }
  \label{tab:params:5}
  \vspace{0.25cm}
  \centering
  \small
  \begin{tabular}{|l|c|c|c|c|c|c|}
    \hline
    Dimension        & 2  & 3  & 5  & 10 & 20  & 40  \\ \hline
    Generations      & 40 & 25 & 28 & 50 & 66  & 80  \\ \hline
    Population Size  & 100 & 120 & 120 & 140 & 200 & 250 \\ \hline
    Populations      & 5 & 5 & 5 & 5 & 5  & 5  \\ \hline
    Iterations       & 10 & 20 & 30 & 30 & 30  & 40  \\ \hline
  \end{tabular}
\end{table}

>>>>

@@

\begin{table}[h!tbp]
  \small
  \caption{Parameters used in the experiments with ten populations
  }
  \label{tab:params:10}
  \vspace{0.25cm}
  \centering
  \small
  \begin{tabular}{|l|c|c|c|c|c|c|}
    \hline
    Dimension        & 2  & 3  & 5  & 10 & 20  & 40  \\ \hline
    Generations      & 40 & 25 & 28 & 50 & 66  & 80  \\ \hline
    Population Size  & 50 & 60 & 60 & 70 & 100 & 125 \\ \hline
    Populations      & \multicolumn{6}{c|}{10} \\ \hline
    Iterations       & 10 & 20 & \multicolumn{3}{c|}{30}  & 40  \\ \hline  
  \end{tabular}
\end{table}
%
\begin{table}[h!tbp]
  \small
  \caption{Parameters used in the experiments with five populations
  }
  \label{tab:params:5}
  \vspace{0.25cm}
  \centering
  \small
  \begin{tabular}{|l|c|c|c|c|c|c|}
    \hline
    Dimension        & 2  & 3  & 5  & 10 & 20  & 40  \\ \hline
    Generations      & 40 & 25 & 28 & 50 & 66  & 80  \\ \hline
    Population Size  & 100 & 120 & 120 & 140 & 200 & 250 \\ \hline
    Populations      & \multicolumn{6}{c|}{5} \\ \hline
    Iterations       & 10 & 20 & \multicolumn{3}{c|}{30}  & 40  \\ \hline
  \end{tabular}
\end{table}
